Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-10-02 paper/paper.tex
new abstract

\begin{abstract}
Full-waveform inversion is an adjoint-based optimization problem in
seismic imaging that processes terabytes of data, often beyond the
memory capacity of most modern computer systems. A common technique to
carry out the adjoint computation in an environment with
less-than-optimal memory is checkpoint-recomputation. In this
technique, a subset of the forward-computation states are stored in
memory checkpoints and the others are recomputed from the stored
states. The compression of checkpoints can increase the number of
checkpoints available, in a given amount of memory, which, in turn,
can reduce the recompute factor, reducing the time-to-solution of the
adjoint computation. This compression, often comes at an additional
computational cost, and an associated loss of precision that must be
accounted for when choosing between compression schemes. In this
paper, we study the effect of compression on checkpoint-recomputation
methods in memory-constrained scenarios for a realistic FWI workload.
\end{abstract}

>>>>

\begin{abstract}
Full-waveform inversion is an adjoint-based optimization problem in seismic
imaging that processes terabytes of data and regularly exceeds the memory
capacity of available computers. A popular strategy to reduce the memory
requirement is data compression, which can reduce the memory
footprint by a certain factor. An alternative is
checkpointing, where data is stored at selected points in
time, and values at other times are recomputed as needed from the last stored state.
This allows arbitrarily large adjoint computations with limited memory, at the cost
of additional recomputations.

In this paper we combine compression and checkpointing for the first
time to compute a realistic full-waveform inversion. The combination of
checkpointing and compression allows
larger adjoint computations compared to using only compression, and
reduces the recomputation overhead significantly compared to using only checkpointing.

\end{abstract}
